%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% This is the documentation for the
% stmhyperref package
%
% Usage
%  - Compile using 'arara stmhyperref.tex'
% 
% Revisions: 2019-10-27 Martin Raedel <martin.raedel@dlr.de>
%                       Initial draft
%               
% Contact:   Martin Raedel,  martin.raedel@dlr.de
%            DLR Lightweight Systems
%          
%                                 __/|__
%                                /_/_/_/  
%            www.dlr.de/fa/en      |/ DLR
%
% Copyright (C) 2019-... DLR Lightweight Systems
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Content                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% --------------------------- 
% Documentclass
% ---------------------------

\documentclass[%
  type=article,%
  layout=koma,%
  %hyperref=true,%
  conditionallox=true,%
  conditionalloxnewpage=false,%
  date=true,%
  %glossaries=true,%
  index=true,%
  listings=true%
]{stmtext}

% ---------------------------
% Build automation
% ---------------------------

% arara: pdflatex: {shell: yes, synctex: yes, interaction: nonstopmode}
% arara: pdflatex: {shell: yes, synctex: yes, interaction: nonstopmode}
% arara: pdflatex: {shell: yes, synctex: yes, interaction: nonstopmode}
% arara: clean: { extensions: [ acn, acr, alg, aux, auxlock, bbl, bcf, blg, dpth, dvi, glg, glo, gls, idx, ilg, ind, ist, kate-swp, lock, lof, log, lol, lot, mw, nlo, out, ps, run.xml, slg, slg*, syg, syg*, syi, syi*, synctex, synctex.gz, tex.backup, tex.kate-swp, toc*, user.adi ] }

% ---------------------------
% Packages
% ---------------------------

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\usepackage[
  styles=true,
  style=stmdefault,
]{stmhyperref}

\usepackage{cleveref}

% ---------------------------
% Doc info
% ---------------------------

\author{Martin R\"{a}del}
\title{stmhyperref package description}
\subtitle{Copyright \copyright{} \the\year{} DLR SY STM\\v\formatdate[versiondatestyle]{\DTMToday}}
\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
This package takes care of handling cross-referencing in \LaTeX{} documents with hypertext links. It loads the underlying base package and offers a modular collection of styles for the representation of hyperlinks. It is build upon the \href{https://ctan.org/pkg/hyperref}{hyperref} package.
\end{abstract}

\tableofcontents

\conditionallistoffigures  % Insert List of Figures if figures are present
\conditionallistoftables   % Insert List of Tables if tables are present
\conditionallistoflistings % Insert List of Listings if listings are present

\section{Usage}% - in the preamble}

\subsection{Load the whole \protect\texttt{stmhyperref} package}
\label{sec:usage:preamble:wholepackage}

\subsubsection{Description}
\label{sec:usage:preamble:wholepackage:description}

This is an interface package which loads the base package and the style choice.

By default the package loads

\begin{itemize}[noitemsep]
  \item \verb+stmhyperrefbase.sty+
  \item \verb+stmhyperrefpdfopts.sty+
  \item \verb+stmhyperrefstyles.sty+
\end{itemize}

See \autoref{sec:usage:preamble:wholepackage:options} for options to change the default package behavior.

\subsubsection{Options}
\label{sec:usage:preamble:wholepackage:options}

\paragraph{Option \protect\textit{styles}} 
\label{sec:usage:preamble:wholepackage:options:styles}

This is a boolean option. Expected values are either \texttt{true} or \texttt{false}. It controls whether to load the predefined styles.

\begin{verbatim}
\usepackage[styles=true|false]{stmhyperref}
\end{verbatim}

\texttt{styles=true} is the default. It is used in case \texttt{styles=false} is not set explicitly.

\paragraph{Option \protect\textit{style}} 
\label{sec:usage:preamble:wholepackage:options:style}

This option value is the equivalent to \cref{sec:usage:preamble:styles:options:style} and is passed through to the underlying package.

\paragraph{Option \protect\textit{pdfopts}} 
\label{sec:usage:preamble:wholepackage:options:pdfopts}

This is a boolean option. Expected values are either \texttt{true} or \texttt{false}. It controls whether to load the predefined pdf view option sets.

\begin{verbatim}
\usepackage[pdfopts=true|false]{stmhyperref}
\end{verbatim}

\texttt{pdfopts=true} is the default. It is used in case \texttt{pdfopts=false} is not set explicitly.

\paragraph{Option \protect\textit{pdfopt}} 
\label{sec:usage:preamble:wholepackage:options:pdfopt}

This option value is the equivalent to \cref{sec:usage:preamble:pdfopts:options} and is passed through to the underlying package.

\subsection{\protect\texttt{stmhyperrefbase}}
\label{sec:usage:preamble:base}

This package loads the underlying base package with some default options that can only be set during initialization.

\subsection{\protect\texttt{stmhyperrefstyles}}
\label{sec:usage:preamble:styles}

\subsubsection{Description}
\label{sec:usage:preamble:styles:description}

This package contains styles for the optical behaviour of internal and external links. Internal links are those inside the document, e.g. references and citations. External links are those to URL's.

\subsubsection{Options}
\label{sec:usage:preamble:styles:options}

\paragraph{Option \protect\textit{style}} 
\label{sec:usage:preamble:styles:options:style}

This is a string option. A list of possible values is shown in \cref{sec:styles}.

\begin{verbatim}
\usepackage[style=stmdefault]{stmhyperrefstyles}
\end{verbatim}

\texttt{style=stmdefault} is the default. It is used in case no other style is set explicitly.

\subsection{\protect\texttt{stmhyperrefpdfopts}}
\label{sec:usage:preamble:pdfopts}

\subsubsection{Description}
\label{sec:usage:preamble:pdfopts:description}

This package contains definitions how to display the resulting document at opening in the viewer.

\subsubsection{Options}
\label{sec:usage:preamble:pdfopts:options}

This is a string option. A list of possible values is listed in \cref{sec:pdfopts}.

\begin{verbatim}
\usepackage[pdfopt=stmdefault]{stmhyperrefpdfopts}
\end{verbatim}

\texttt{style=stmdefault} is the default. It is used in case no other style is set explicitly. A list of possible values is shown in \autoref{sec:pdfopts}.

\section{Styles}
\label{sec:styles}

There are different predefined styles available to format your hypertext.

\subsection{\protect\texttt{default}}
\label{sec:styles:default}

This loads the default style from the underlying base package and does not apply individual styles.

\subsection{\protect\texttt{stmdefault}}
\label{sec:styles:stmdefault}

This loads the color definitions for links, citations and URL's from the \texttt{stmcolor} package and applies them.

\subsection{\protect\texttt{colorlinkexternalblueinternalblack}}
\label{sec:styles:colorlinkexternalblueinternalblack}

Please take the style information directly from \cref{sec:code:styles}.

\subsection{\protect\texttt{colorlinkallblack}}
\label{sec:styles:colorlinkallblack}

Please take the style information directly from \cref{sec:code:styles}.

\subsection{\protect\texttt{colorlinkallblue}}
\label{sec:styles:colorlinkallblue}

Please take the style information directly from \cref{sec:code:styles}.

\section{\protect\texttt{pdfopt} sets}
\label{sec:pdfopts}

There are different predefined options sets available to configure the pdf view settings.

\subsection{\protect\texttt{default}}
\label{sec:pdfopts:default}

Please take the style information directly from \cref{sec:code:pdfopts}.

\subsection{\protect\texttt{stmdefault}}
\label{sec:pdfopts:stmdefault}

Please take the style information directly from \cref{sec:code:pdfopts}.

\subsection{\protect\texttt{viewfitwmenuwtoolbarwobookmarksopen}}
\label{sec:pdfopts:viewfitwmenuwtoolbarwobookmarksopen}

Please take the style information directly from \cref{sec:code:pdfopts}.

\printstmindex

\newpage
\appendix

\section{The code}
\label{sec:code}

\subsection{\protect\texttt{stmhyperref.sty}}
\label{sec:code:main}

\lstinputlisting[
  style=texpackagedocstyle,%
]{../../tex/latex/stmhyperref/stmhyperref.sty}

\subsection{\protect\texttt{stmhyperrefbase.sty}}
\label{sec:code:base}

\lstinputlisting[
  style=texpackagedocstyle,%
]{../../tex/latex/stmhyperref/stmhyperrefbase.sty}

\subsection{\protect\texttt{stmhyperrefpdfopts.sty}}
\label{sec:code:pdfopts}

\lstinputlisting[
  style=texpackagedocstyle,%
]{../../tex/latex/stmhyperref/stmhyperrefpdfopts.sty}

\subsection{\protect\texttt{stmhyperrefstyles.sty}}
\label{sec:code:styles}

\lstinputlisting[
  style=texpackagedocstyle,%
]{../../tex/latex/stmhyperref/stmhyperrefstyles.sty}

\end{document}
